Spatial Analysis

### 2021-06-15 Scripts/spatial_analisis.Rmd
Final updates to inddex

# Plot to make sure makes sense (Picasso syle)
grid_eez_sf %>%
  st_simplify(preserveTopology = TRUE, dTolerance = 10000) %>% #0.1 for paper
  ggplot() +
  geom_sf(aes(color = state), alpha = 0.3)

>>>>

# Plot to make sure makes sense (Picasso syle)
grid_eez_sf %>%
  st_simplify(preserveTopology = TRUE, dTolerance = 10000) %>% #0.1 for paper
  ggplot() +
  geom_sf(aes(color = state), alpha = 0.3) +
  scale_color_manual(values = state_pallet)
